What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
reformatted that mulan table
shared report just tells us what j48 words are shared
some table changes

\begin{table*}[h]
	\caption{Qualities and associated signifiers – Wordnet version (\textsf{exp2})}
	\centering
	\label{tbl:wnsig}
\begin{tabular}{c|p{9cm}}
\toprule
\textbf{Label} & \textbf{Related terms} \\
\midrule
\emph{Maintainability} &
testability changeability analyzability stability maintain maintainable modularity modifiability understandability + interdependent dependency encapsulation decentralized modular\\ \hline
\emph{Functionality} &
security compliance accuracy interoperability suitability functional practicality functionality + compliant exploit certificate secured “buffer overflow” policy malicious trustworthy vulnerable vulnerability accurate secure vulnerability correctness accuracy\\ \hline
\emph{Portability} &
conformance adaptability replaceability installability portable movableness movability portability + specification migration standardized l10n localization i18n internationalization documentation interoperability transferability\\ \hline
\emph{Efficiency} &
“resource behaviour” “time behaviour” efficient efficiency + performance profiled optimize sluggish factor penalty slower faster slow fast optimization\\ \hline
\emph{Usability} &
operability understandability learnability useable usable serviceable usefulness utility useableness usableness serviceableness serviceability usability + gui accessibility menu configure convention standard feature focus ui mouse icons ugly dialog guidelines click default human convention friendly user screen interface flexibility\\ \hline
\emph{Reliability} &
“fault tolerance” recoverability maturity reliable dependable responsibleness responsibility reliableness reliability dependableness dependability + resilience integrity stability stable crash bug fails redundancy error failure\\ 
\bottomrule
\end{tabular}
\end{table*}

@@

% Cribbed from: 
% src/validate/latex-out/best-learner-per-project-roc-table.tx
\begin{table*}
\centering
\begin{tabular}{ccc|rrrr}
Label & Project & Learner & ROC & ZeroR Acc. & ZeroR. Diff & Fmeasure\\
\hline
portability &  mysql &  NaiveBayesMultinomial &  0.74 &  58.53 &  11.43 &  0.70  \\ 
efficiency &  mysql &  NaiveBayes &  0.67 &  93.69 &  -7.68 &  0.88 \\ 
reliability &  mysql &  NaiveBayes &  0.73 &  83.11 &  -12.80 &  0.74 \\ 
functionality &  mysql &  DMNBtext &  0.81 &  54.44 &  21.67 &  0.76 \\ 
maintainability &  mysql &  DMNBtext &  0.78 &  76.62 &  3.41 &  0.75 \\ 
usability &  mysql &  NaiveBayes &  0.75 &  94.54 &  -5.80 &  0.90  \\ 
%total & mysql & NaibeBayes & 0.75 & 
 \hline 
portability &  maxdb &  NaiveBayes &  0.84 &  77.12 &  2.06 &  0.80 \\ 
efficiency &  maxdb &  NaiveBayes &  0.62 &  88.43 &  -11.31 &  0.79 \\ 
reliability &  maxdb &  DMNBtext &  0.84 &  89.46 &  3.86 &  0.92  \\ 
functionality &  maxdb &  NaiveBayes &  0.67 &  91.26 &  -6.94 &  0.86  \\ 
maintainability &  maxdb &  NaiveBayes &  0.70 &  79.43 &  -9.25 &  0.72  \\ 
usability &  maxdb &  NaiveBayes &  0.56 &  95.37 &  -4.37 &  0.91  \\ 
 \hline 
\end{tabular}
\caption{Per label, per project, the best learner for that label}
\label{tab:best-learner-per-tag}
\end{table*}

@@

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=.99\textwidth]{small-mysql-time-smear-plot-Equal}
  \caption{MySQL 3.23: Labelled topics over time, continuous topics are trends that occur across time}
  \label{fig:mysql}
\end{figure*}

>>>>

\begin{table*}
	\caption{Qualities and associated signifiers – Wordnet version (\textsf{exp2})}
	\centering
	\label{tbl:wnsig}
\begin{tabular}{c|p{9cm}}
\toprule
\textbf{Label} & \textbf{Related terms} \\
\midrule
\emph{Maintainability} &
testability changeability analyzability stability maintain maintainable modularity modifiability understandability + interdependent dependency encapsulation decentralized modular\\ \hline
\emph{Functionality} &
security compliance accuracy interoperability suitability functional practicality functionality + compliant exploit certificate secured “buffer overflow” policy malicious trustworthy vulnerable vulnerability accurate secure vulnerability correctness accuracy\\ \hline
\emph{Portability} &
conformance adaptability replaceability installability portable movableness movability portability + specification migration standardized l10n localization i18n internationalization documentation interoperability transferability\\ \hline
\emph{Efficiency} &
“resource behaviour” “time behaviour” efficient efficiency + performance profiled optimize sluggish factor penalty slower faster slow fast optimization\\ \hline
\emph{Usability} &
operability understandability learnability useable usable serviceable usefulness utility useableness usableness serviceableness serviceability usability + gui accessibility menu configure convention standard feature focus ui mouse icons ugly dialog guidelines click default human convention friendly user screen interface flexibility\\ \hline
\emph{Reliability} &
“fault tolerance” recoverability maturity reliable dependable responsibleness responsibility reliableness reliability dependableness dependability + resilience integrity stability stable crash bug fails redundancy error failure\\ 
\bottomrule
\end{tabular}
\end{table*}

@@

% Cribbed from: 
% src/validate/latex-out/best-learner-per-project-roc-table.tx
\begin{table*}
\centering
\begin{tabular}{ccc|rrrr}
\toprule
Label & Project & Learner & ROC & ZeroR Acc. & ZeroR. Diff & Fmeasure\\
\midrule
portability &  MySQL &  NaiveBayesMultinomial &  0.74 &  58.53 &  11.43 &  0.70  \\ 
efficiency &  MySQL &  NaiveBayes &  0.67 &  93.69 &  -7.68 &  0.88 \\ 
reliability &  MySQL &  NaiveBayes &  0.73 &  83.11 &  -12.80 &  0.74 \\ 
functionality &  MySQL &  DMNBtext &  0.81 &  54.44 &  21.67 &  0.76 \\ 
maintainability &  MySQL &  DMNBtext &  0.78 &  76.62 &  3.41 &  0.75 \\ 
usability &  MySQL &  NaiveBayes &  0.75 &  94.54 &  -5.80 &  0.90  \\ 
%total & MySQL & NaibeBayes & 0.75 & 
 \hline 
portability &  MaxDB &  NaiveBayes &  0.84 &  77.12 &  2.06 &  0.80 \\ 
efficiency &  MaxDB &  NaiveBayes &  0.62 &  88.43 &  -11.31 &  0.79 \\ 
reliability &  MaxDB &  DMNBtext &  0.84 &  89.46 &  3.86 &  0.92  \\ 
functionality &  MaxDB &  NaiveBayes &  0.67 &  91.26 &  -6.94 &  0.86  \\ 
maintainability &  MaxDB &  NaiveBayes &  0.70 &  79.43 &  -9.25 &  0.72  \\ 
usability &  MaxDB &  NaiveBayes &  0.56 &  95.37 &  -4.37 &  0.91  \\ 
 \hline 
\end{tabular}
\caption{Per label, per project, the best learner for that label}
\label{tab:best-learner-per-tag}
\end{table*}

@@

\begin{comment}

@@

\begin{table*}
\centering
\begin{tabular}{l|ccc|ccc}
\toprule
  & MySQL & MySQL & MySQL &                         MaxDB & MaxDB & MaxDB  \\ 
Performance Metric  & BR & CLR & HOMER &                              BR & CLR & HOMER \\

\midrule
%\hline \\

example-Accuracy & 0.45 & 0.40 & 0.50 &           0.49  &  0.47  &  0.51 \\

example-Fmeasure & 0.56 & 0.48 & 0.59 &           0.55  &  0.50  &  0.53 \\

example-HammingLoss & 0.24 & 0.19 & 0.18 &        0.19  &  0.14  &  0.14 \\

example-Precision & 0.50 & 0.51 & 0.60 &          0.50  &  0.49  &  0.53 \\

example-Recall & 0.65 & 0.46 & 0.58 &             0.61  &  0.50  &  0.53 \\

example-SubsetAccuracy & 0.19 & 0.24 & 0.31 &     0.40  &  0.43  &  0.45 \\

label-macro-ROC & 0.74 & 0.66 & 0.64 &            NaN  &  NaN  &  NaN    \\

label-macro-F1 & 0.46 & 0.30 & 0.43 &             0.32  &  0.19  &  0.23 \\

label-macro-Precision & 0.41 & 0.41 & 0.49 &      0.29  &  0.31  &  0.32 \\

label-macro-Recall & 0.56 & 0.26 & 0.40 &         0.38  &  0.15  &  0.20 \\

label-micro-ROC & 0.81 & 0.81 & 0.77 &            0.76  &  0.66  &  0.62 \\

label-micro-F1 & 0.59 & 0.53 & 0.61 &             0.39  &  0.27  &  0.34 \\

label-micro-Precision & 0.51 & 0.69 & 0.66 &      0.34  &  0.42  &  0.49 \\

label-micro-Recall & 0.68 & 0.43 & 0.56 &         0.47  &  0.21  &  0.26 \\

rank-AvgPrecision & 0.76 & 0.77 & 0.69 &          0.54  &  0.57  &  0.54 \\

rank-Coverage & 1.51 & 1.47 & 1.94 &              1.40  &  1.23  &  1.43 \\

rank-One-error & 0.40 & 0.39 & 0.47 &             0.81  &  0.79  &  0.81 \\

rank-Ranking Loss & 0.19 & 0.18 & 0.27 &          0.41  &  0.35  &  0.41 \\ 
\hline
\end{tabular}
\caption{MySQL and MaxDB Mulan results per Multi-Label learner}
\end{table*}

@@

\begin{figure*}[h]
  \centering
  \includegraphics[width=.99\textwidth]{small-mysql-time-smear-plot-Equal}
  \caption{MySQL 3.23: Labelled topics over time, continuous topics are trends that occur across time}
  \label{fig:mysql}
\end{figure*}
